An important task towards achieving fault-tolerant quantum computation is
finding efficient decoding schemes.
Since error propagation on non-clifford gates cannot be simulated efficiently
\cite{gottesmanFaultTolerant}, and we are only given syndromes by our ECC,
the decoding scheme must be able to compute occurred 
errors from syndromes in time before the quantum algorithm our computer intends 
to calculate reaches a non-Clifford operation. This ideally requires very fast 
classical computation of the syndrome decoding.

In this chapter, we will introduce some of the main decoding schemes for
varying types of quantum error correction codes.

\subsection{Decoders for Surface/Toric codes}
Syndromes on the surface/toric code are a set of nodes and
faces on the code's Tanner graph. The node ancilla syndromes correspond to
Z errors, while the face ancilla syndromes correspond to X errors.
Since neighboring errors will trigger an ancilla that is between 
both errors twice, a chain of errors will only appear as two ancilla
syndrome bits being flipped at its borders.
The task of a decoding scheme for a surface/toric code is thus to
find the shortest paths between node pairs/face pairs, since the most likely
chain of errors to occur given a $<50\%$ physical error rate is the 
shortest one.

In practice, decoders for surface/toric codes only need to be able to
match nodes, since the matching of faces is just matching nodes on the 
dual graphs and the resulting data qubit errors can just be joined
(i.e. if an edge is found to have an error on both the X graph as well as the
dual Z graph, we know a Y error has occurred on that edge/data-qubit).
An example of a distance 5 surface code with two Z errors, one X error and
one Y error is shown in Figure \ref{fig: surface_code}.
As with the ring code, the decoding problem can be seen as either the
solution of Equation \ref{eq: pcm} for a minimum weight $\vec{v}_{error}$
or as a graph-matching problem.
\input{chapterstex/decodingschemes/surfacetoric/mwpm}
\input{chapterstex/decodingschemes/surfacetoric/unionfind}

\subsection{Color code decoders}
Unlike the surface and toric codes, in the color code the 
data qubits sit on the graph's nodes, and the ancillas on the 
graph's faces. Decoding the color code entails matching 
three differently colored faces to their enclosed nodes.
This is a significantly more challenging task than
decoding the surface or toric code, since optimal three-colored graph hyperface matching 
is an NP-hard problem \cite{delfosse}.
\input{chapterstex/decodingschemes/color/lookup}
\input{chapterstex/decodingschemes/color/lifting}